Automated verification of stand-alone solar photovoltaic systems

### 2018-11-19 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
With declining costs and increasing performance, the deployment of renewable energy systems is growing in both developed and developing countries. Particular attention is being given to stand-alone solar photovoltaic systems in rural areas or where grid extension is not feasible. Tools to evaluate the design and validate electrification projects are available; however, those tools are based on simulation that do not cover all the aspects of the design space. Automated verification using model checking, however, has proven to be an effective technique to program verification. However, any kind of system can be verified by formal methods, including the most complex ones. Here each component of a stand-alone solar photovoltaic system, as solar panel, charge controller, battery, inverter, and electric load, were encoded into a mathematical model, and a algorithm using automated software model checking was created in order to validate its design from a formal verification perspective. Case studies, from real photovoltaic systems deployed in five different sites, ranging from $700$ W to $1,200$ W, were used to evaluate the proposed technique, always comparing the results with the specialized simulation tool HOMER Pro. Data from practical applications show the effectiveness of the obtained results, where specific conditions that lead to failures in a photovoltaic solar system are only detected with the proposed verification method.
%Experimental results show that the proposed approach can find situations where the sized solar photovoltaic system fails to meet the requirements demanded to electrify a house, and that simulation made with commercial tools can not find the same failure. \textcolor{red}{Data from practical application of solar systems prove the results obtained by the proposed approach... this last sentence should be stronger to emphasise your main contribution... maybe you could update this after obtaining the experimental results...}
\end{abstract}

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
With declining costs and increasing performance, the deployment of renewable energy systems is growing in both developed and developing countries. Particular attention is being given to stand-alone solar photovoltaic systems in rural areas or where grid extension is not feasible. Tools to evaluate the design and validate electrification projects are available; however, those tools are based on simulations that do not cover all the aspects of the design space. Automated verification using model checking, however, has proven to be an effective technique to program verification. Here each component of a stand-alone solar photovoltaic system, as solar panel, charge controller, battery, inverter, and electric load, are encoded into a mathematical model, and a software model checking algorithm was developed to verify its design from a formal perspective. Case studies, from real photovoltaic systems deployed in five different sites, ranging from $700$ W to $1,200$ W, were used to evaluate the proposed technique, always comparing the results with the specialized simulation tool HOMER Pro. Data from practical applications show the effectiveness of the obtained results, where specific conditions that lead to failures in a photovoltaic solar system are only detected with the proposed verification method.
%Experimental results show that the proposed approach can find situations where the sized solar photovoltaic system fails to meet the requirements demanded to electrify a house, and that simulation made with commercial tools can not find the same failure. \textcolor{red}{Data from practical application of solar systems prove the results obtained by the proposed approach... this last sentence should be stronger to emphasise your main contribution... maybe you could update this after obtaining the experimental results...}
\end{abstract}
